Supplement to ``{\mytitle}''

### 2024-03-02 si/confidenceIntervals.Rnw
Fixed units for parameters, other minor typos, and response to editors

  Process noise & $\sigmaProc: \mathrm{Epi}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_epi') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(upper), 3)})$ 
\\
\hline

  Process noise & $\sigmaProc: \mathrm{End}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_end') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(upper), 3)})$ 
\\
\hline

@@

  } else {
    tmp_df <- h2_profiles %>% 
      filter(prof_var == p) %>% 
      # filter(logLik >= -21957.26 - 4) %>%
      arrange(p)

@@

 Human to water shedding & $\Wshed$ & $\Sexpr{myround(h2_mles['Mu'], 1)}$
   &
  $(\Sexpr{myround(h2_plots_lb['Mu'], 1)}, \Sexpr{myround(h2_plots_ub['Mu'], 1)})$ 
\\
\hline

 Water to Human Infection & $\beta_W$ & $\Sexpr{myround(h2_mles['BetaW'], 3)}$
   &
  $(\Sexpr{myround(h2_plots_lb['BetaW'], 3)}, \Sexpr{myround(h2_plots_ub['BetaW'], 3)})$ 
\\
\hline

@@

Human to Human Infection & $\transmission$ & $\Sexpr{signif(h2_mles['Beta'], 3)}$\textsuperscript{*}
   &
  $[0, \Sexpr{signif(h2_plots_ub['Beta'], 3)})$ 
\\
\hline

Immunity (yr) & $\muRS^{-1}$ & $\Sexpr{signif(1/h2_mles['sigma'], 3)}$\textsuperscript{*}
   &
  $(\Sexpr{signif(1/h2_plots_ub['sigma'], 3)}, \inf)$ 
\\
\hline

@@

H3_profiles_long <- H3_profiles %>%
  select(prof_var, logLik, logLik_se, all_of(paste0(prof_params, '1'))) %>%
  rename_with(~ sub("1$", "", .x)) %>%
  mutate(mu_B = mu_B / 52) %>% 
  select(-epsilon, -XthetaA) %>% 
  pivot_longer(
    cols = -c(prof_var, logLik, logLik_se),
    names_to = 'variable',
    values_to = 'value'
  ) %>%
  filter(variable == prof_var) %>%
  group_by(prof_var, value) %>%
  slice_max(order_by = logLik, n = 1)

H3_remaining_long <- H3_profiles %>% 
  select(prof_var, logLik, logLik_se, epsilon1, XthetaA1) %>% 
  rename(epsilon = epsilon1, XthetaA = XthetaA1) %>% 
  mutate(XthetaA = sqrt(XthetaA)) %>%
  mutate(epsilon = epsilon^2) %>%
  pivot_longer(
    cols = -c(prof_var, logLik, logLik_se),
    names_to = 'variable',
    values_to = 'value'
  ) %>%
  filter(variable == prof_var) %>%
  group_by(prof_var, value) %>%
  slice_max(order_by = logLik, n = 2)

@@

\begin{figure}[ht]
<<m3Profs, fig.height=4.6, fig.width=5.8, echo=FALSE, warning=FALSE, message=FALSE>>=
h3_plots <- list()
for (i in 1:length(prof_params)) {
  p = prof_params[i]
  if (p == 'mu_B') {
    my_lab <- TeX('$\\delta_W$')
  } else if (p == 'XthetaA') {
    my_lab <- TeX('$\\sqrt{\\epsilon_W}$')
  } else if (p == 'thetaI') {
    my_lab <- TeX('$\\mu_W$')
  } else if (p == 'lambdaR') {
    my_lab <- TeX('$a$')
  } else if (p == 'r') {
    my_lab <- TeX('$r$')
  } else if (p == 'std_W') {
    my_lab <- TeX('$\\sigma$')
  } else if (p == 'epsilon') {
    my_lab <- TeX('$\\rho$')
  } else if (p == 'k') {
    my_lab <- TeX('$\\psi$')
  }

@@

 Process Noise & $\sigmaProc$ & $\Sexpr{myround(h3_mles %>% filter(prof_var == 'std_W') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'std_W') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'std_W') %>% pull(upper), 3)})$ 
\\
\hline

 Water Survival (wk) & $\Wremoval^{-1}$ & $\Sexpr{myround(52 / (h3_mles %>% filter(prof_var == 'mu_B') %>% pull(value)), 3)}$
   &
  $(\Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(upper)), 3)}, \Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(lower)), 3)})$ 
\\
\hline

 Human to Water Shedding & $\Wshed$ & $\Sexpr{signif(h3_mles %>% filter(prof_var == 'thetaI') %>% pull(value), 3)}$
   &
  $(\Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(lower), 3)}, \Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(upper), 3)})$ 
\\
\hline

>>>>

  Process noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{Epi}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_epi') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(upper), 3)})$ 
\\
\hline

  Process noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{End}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_end') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(upper), 3)})$ 
\\
\hline

@@

  } else if (p == 'Mu') {

    tmp_df <- h2_profiles %>% 
      filter(prof_var == p) %>% 
      # filter(logLik >= -21957.26 - 4) %>%
      arrange(p)

    gg_tmp <- ggplot() + 
      geom_point(
        data = h2_profiles %>% 
          filter(prof_var == p) %>% 
          filter(.data[[p]] <= max_x & .data[[p]] >= min_x) ,
        aes(x = .data[[p]] / 52, y = logLik)
      ) + 
      geom_function(fun = profile_like) + 
      geom_vline(xintercept = lower_bound / 52, linetype = 'dashed') + 
      geom_vline(xintercept = upper_bound / 52, linetype = 'dashed') + 
      geom_vline(xintercept = max_profile$maximum / 52, col = 'blue') + 
      labs(y = 'Log-Likelihood', title = my_lab) + 
      theme(
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 10)
      ) +
      theme_bw() +
      # scale_y_continuous(limits = c(-21963, -21957)) + 
      scale_y_continuous(limits = c(max(h2_profiles$logLik)-6, max(h2_profiles$logLik))) +
      scale_x_continuous(limits = c(min_x/52, max_x/52)) + 
      theme(
        axis.title.x = element_blank(), 
        plot.title = element_text(
          hjust = 0.5, size = 8, margin = margin(t = 0, unit = "pt")
        ),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 6.5),
        plot.margin = margin(5.5, 3, 0, -1, unit = 'pt')
      )

    if (i %in% c(1, 4)) {
      h2_plots[[p]] <- gg_tmp
    } else {
      h2_plots[[p]] <- gg_tmp + theme(
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.title.y = element_blank()
      )
    }
  } else {
    tmp_df <- h2_profiles %>% 
      filter(prof_var == p) %>% 
      # filter(logLik >= -21957.26 - 4) %>%
      arrange(p)

@@

 Human to water shedding {\small (wk\textsuperscript{-1})} & $\Wshed$ & $\Sexpr{myround(h2_mles['Mu']/52, 1)}$
   &
  $(\Sexpr{myround(h2_plots_lb['Mu']/52, 1)}, \Sexpr{myround(h2_plots_ub['Mu']/52, 1)})$ 
\\
\hline

 Water to Human Infection {\small (yr\textsuperscript{-1})} & $\beta_W$ & $\Sexpr{myround(h2_mles['BetaW'], 3)}$
   &
  $(\Sexpr{myround(h2_plots_lb['BetaW'], 3)}, \Sexpr{myround(h2_plots_ub['BetaW'], 3)})$ 
\\
\hline

@@

Human to Human Infection {\small (yr\textsuperscript{-1})} & $\transmission$ & $\Sexpr{signif(h2_mles['Beta'], 3)}$\textsuperscript{*}
   &
  $[0, \Sexpr{signif(h2_plots_ub['Beta'], 3)})$ 
\\
\hline

Immunity {\small (yr)} & $\muRS^{-1}$ & $\Sexpr{signif(1/h2_mles['sigma'], 3)}$\textsuperscript{*}
   &
  $(\Sexpr{signif(1/h2_plots_ub['sigma'], 3)}, \inf)$ 
\\
\hline

@@

H3_profiles_long <- H3_profiles %>%
  select(prof_var, logLik, logLik_se, all_of(paste0(prof_params, '1'))) %>%
  rename_with(~ sub("1$", "", .x)) %>%
  mutate(mu_B = mu_B / 52) %>% 
  mutate(thetaI = thetaI / 52) %>% 
  mutate(std_W =  std_W * sqrt(52)) %>%
  select(-epsilon, -XthetaA) %>% 
  pivot_longer(
    cols = -c(prof_var, logLik, logLik_se),
    names_to = 'variable',
    values_to = 'value'
  ) %>%
  filter(variable == prof_var) %>%
  group_by(prof_var, value) %>%
  slice_max(order_by = logLik, n = 1)

H3_remaining_long <- H3_profiles %>% 
  select(prof_var, logLik, logLik_se, epsilon1, XthetaA1) %>% 
  rename(epsilon = epsilon1, XthetaA = XthetaA1) %>% 
  mutate(XthetaA = sqrt(XthetaA)) %>%
  mutate(epsilon = epsilon^2) %>%
  # mutate(std_W =  std_W * sqrt(52)) %>% 
  pivot_longer(
    cols = -c(prof_var, logLik, logLik_se),
    names_to = 'variable',
    values_to = 'value'
  ) %>%
  filter(variable == prof_var) %>%
  group_by(prof_var, value) %>%
  slice_max(order_by = logLik, n = 2)

@@

\begin{figure}[ht]
<<m3Profs, fig.height=4.6, fig.width=5.8, echo=FALSE, warning=FALSE, message=FALSE>>=
h3_plots <- list()
for (i in 1:length(prof_params)) {
  p = prof_params[i]
  if (p == 'mu_B') {
    my_lab <- TeX('$\\delta_W$')
  } else if (p == 'XthetaA') {
    my_lab <- TeX('$\\sqrt{\\epsilon_W}$')
  } else if (p == 'thetaI') {
    my_lab <- TeX('$\\mu_W$')
  } else if (p == 'lambdaR') {
    my_lab <- TeX('$a$')
  } else if (p == 'r') {
    my_lab <- TeX('$r$')
  } else if (p == 'std_W') {
    my_lab <- TeX('$\\sigma_{proc}$')
  } else if (p == 'epsilon') {
    my_lab <- TeX('$\\rho$')
  } else if (p == 'k') {
    my_lab <- TeX('$\\psi$')
  }

@@

 Process Noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc$ & $\Sexpr{myround((h3_mles %>% filter(prof_var == 'std_W') %>% pull(value)) * sqrt(52), 3)}$
   &
  $(\Sexpr{myround((all_ci %>% filter(prof_var == 'std_W') %>% pull(lower)), 3)}, \Sexpr{myround((all_ci %>% filter(prof_var == 'std_W') %>% pull(upper)), 3)})$ 
\\
\hline

 Water Survival {\small (wk)} & $\Wremoval^{-1}$ & $\Sexpr{myround(52 / (h3_mles %>% filter(prof_var == 'mu_B') %>% pull(value)), 3)}$
   &
  $(\Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(upper)), 3)}, \Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(lower)), 3)})$ 
\\
\hline

 Human to Water Shedding {\small $\frac{\mathrm{km^2}}{\mathrm{wk}}$} & $\Wshed$ & $\Sexpr{signif((h3_mles %>% filter(prof_var == 'thetaI') %>% pull(value))/52, 3)}$
   &
  $(\Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(lower), 3)}, \Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(upper), 3)})$ 
\\
\hline
